\Large \bf \Toolname: Precise False Sharing Detection for COTS Binaries

### 2014-11-05 HotOS'15/paper.tex
improved the 'key insight' portion of the intro. Still a lot of work to do, but heading to bed.

In this work, we present \Toolname{}, a system for precisely detecting and diagnosing false sharing
in multi-threaded, commercial off-the-shelf (COTS) binaries. The key insights of our approach is that
it iteratively discovers and specializes instrumentation to detect false sharing at increasingly finer
granularities. Our work addresses three limitations of prior work:
\begin{enumerate}
\item They introduce extra cache coherency traffic, which limits scalability and hides performance
problems. The extra traffic introduced comes from the mechanisms used to track cache line ownership.

@@

\paragraph{Contributions}
This paper makes the following contributions:
\begin{itemize}
\item It presents \Toolname{}, a software-only framework that dynamically and precisely diagnoses
false sharing  in multi-threaded, CTOS binaries. We believe that operating directly on binaries is
important because it allows one to verify observed performance problems using the same binaries
that are running in a production environment.

@@

At a high-level, \Toolname{} follows the same principle as Plastic \cite{Plastic} and SHERIFF \cite{SHERIFF}: it detects
false sharing at coarse granularity and then verifies cases of false sharing at a finer granularity. Unlike other approaches,
\Toolname{} repeats this process by incrementally refining the detection granularity, and by selectively instrumenting only
that code that appears to trigger false sharing.

@@

>>>>

In this work, we present \Toolname{}, a system for precisely detecting and diagnosing false sharing
in multi-threaded applications. \Toolname{} uses dynamic binary translation (DBT) and shadow memory
to instrument and detect false sharing in commercial off-the-shelf (COTS) binaries.  The key insight of our
approach is that accesses to shadow memory can be used as a proxy for accesses to actual memory. By 
detecting contention on proxied accesses, we can establish beliefs about the sources of false sharing. These
beliefs are strenghtened and eventually verified by specializing code to proxy memory accesses at increasingly
finer granularities.

Our work addresses three limitations of prior work:
\begin{enumerate}
\item They introduce extra cache coherency traffic, which limits scalability and hides performance
problems. The extra traffic introduced comes from the mechanisms used to track cache line ownership.

@@

\paragraph{Contributions}
This paper makes the following significant contributions:
\begin{itemize}
\item It presents \Toolname{}, a software-only framework that dynamically and precisely diagnoses
false sharing  in multi-threaded, CTOS binaries. We believe that operating directly on binaries is
important because it allows one to verify observed performance problems using the same binaries
that are running in a production environment.

@@

At a high-level, \Toolname{} follows the same principle as Plastic \cite{Plastic} and SHERIFF \cite{SHERIFF}: it detects
false sharing at a coarse granularity and then verifies detected cases at a finer granularity. Unlike other approaches,
\Toolname{} repeats this process by incrementally refining the detection granularity, and by selectively instrumenting only
that code that appears to trigger false sharing. Whereas Plastic and SHERIFF use page-granularity detection, \Toolname{}
is able to vary the granularity over time using a shadow memory. The key insight of our approach is that accesses to
shadow memory at varying granularities can be used as a proxy for accesses to actual memory.

\Toolname{} operates as follows:
\begin{enumerate}
\item Choose 
\end{enumerate}

@@

\subsection{Proxy Memory and Tagged Reads}\label{sec:proxymem}
